Estimation of the road traffic sound levels based on Non-Negative Matrix Factorization

### 2017-12-20 article/articleApplied.tex
continuation of the results part

\section{Introduction}
\subsection{Related work}
With the introduction of the European Directive 2002/EC/49, cities over 100 000 inhabitants have to produce road traffic noise maps. Theses maps allow to estimate the number of city dwellers exposed to high noise levels and to draw up action plans to reduce it as too long exposures to these noises can generate health problems \cite{who_burden_2017}. These maps are the result of a simulation process based on the estimation of the traffic density on the main roads and the use of sound propagation techniques. They express $L_ {DEN}$ and $L_N$, which are \textit{Day-Evening-Night} and \textit{Night} equivalent A-weighted sound levels respectively. However, these maps introduce lot of uncertainty generated by the numerical tools \cite{van_leeuwen_noise_2015}, by the different calculation methodologies used \cite{leroy_uncertainty_2010}\cite{garg_critical_2014} or even by the calculation procedure of the number of inhabitants exposed to noise \cite{king_implementation_2011}. In addition, the usual road traffic noise maps are static, aggregating the exposure on the two indicators $L_{DEN}$ and $L_N$, thus ignoring the sound levels evolution throughout the day. Since the creation of road traffic noise maps entails long data collection and calculation times, the use of acoustic measurements could facilitate their updating or even the generation of dynamic maps \cite{wei_dynamic_2016}. These measurements can be performed at fixed stations spread all over the cities \cite{Mioduszewski} \cite{mietlicki2012innovative}, which would lead to the availability of the long-term evolution of the traffic noise levels. It can also be performed with  mobile stations \cite{can_exploring_2012} \cite{manvell2004sadmam} covering a larger area with fewer sensors but also sparse time periods. %The clustering between mobile and fixed measurements has been studied in \cite{can_measurement_2014}. \ml{je ne vois pas l'intéret de cette dernière phrase}

%\begin{figure*}
%    \centering
%    \subfigure[]{\label{fig:blocDiagramNMF}
%    \includegraphics[width=.45\linewidth]{../image/bloc_diagram_NMF_EN.pdf}}
%    \subfigure[]{\label{fig:blocDiagramFilter}	\includegraphics[width=.45\linewidth]{../image/bloc_diagram_filtrage_EN.pdf}}
%    \caption{Block diagrams summed up the different step of the process for the frequency low-pass filter \ref{fig:blocDiagramFilter} and for NMF \ref{fig:blocDiagramNMF}.}
%    \label{fig:blocDiagram}
%\end{figure*}

Currently, sensor networks in cities are spread for multiple applications (air quality assessment, measurement of meteorological parameters, ...), including the assessment of urban noise levels. DYNAMAP project \cite{dynamap_2016} studied the establishment and feasibility of such installations. It focuses on sensor installations on specific roads at the city scale in Milan and Rome \cite{bellucci_life_2017}. In a similar way, but reduced to few neighborhoods, the CENSE project\footnote{\url{http://cense.ifsttar.fr/}} \cite{} aims to combine \textit{in situ} observations, from a sensor network, and numerical data, from noise modeling, through data assimilation techniques.

If sensors networks could improve road traffic noise estimation compared with simulated maps, the issue of the correct estimation from  measurements of the traffic sound level is still unsolved \cite{Mioduszewski}. Indeed, the urban sound environment is a complex environment gathering lots of different sounds (car passages, voices, bird's whistles, car horn \dots) that can overlap. Consequently, the traffic sound level estimation based on measurements is not trivial task.
Many recent works have focused on the detection or recognition tasks of environmental sounds without distinction between them\cite{heittola_sound_2011}, \cite{defreville_automatic_2006}, \cite{dufaux_automatic_2000}, \cite{chu_environmental_2009}. A two step process is generally followed : describe the audio files with a set of features (Spectrum Gravity Spectrum, harmonicity, Mel-Frequency Cepstral Coefficient \dots) and classify them with the help of classifiers (Support Vector Machines, Gaussian Mixture Models, Hidden Markov Model, Artifical Neural Networks). A description of there features and classifiers can be found in \cite{cowling_comparison_2003} and their application can be found in \cite{shen_environmental_2012}, \cite{beritelli_pattern_2008}, \cite{couvreur_automatic_2004}. Recently, an Anomalous Noise Events Detector has been generated in \cite{socoro_anomalous_2017} to detect the sound sources from labeled recordings that are not related to the traffic component in order not to take them into account on the estimation of the traffic sound level. If the detection of the road traffic noise is good, the detection of theses anomalous noise events stay weak and no information on the improvement on the estimation of the traffic nous level are presented.

@@

We propose in this paper a method based on the Non-Negative Matrix Factorization (NMF) technique to estimate the global, $\tilde{L}_{p,traffic}$, and the 1-s equivalent, $\tilde{p}_{1s,traffic}$ sound level of the traffic through the supervised and the semi-supervised approaches. To validate this approach, we consider a corpus of simulated scenes artificially created with the simulator software \textit{simScene}. The use of simulated sound scenes is necessary as it offers a full control on the design of the scenes and the knowledge of the exact contribution of the traffic component which would hardly be extracted from a recording of an urban scene ($L_{p,traffic}$ and $p_{1s,traffic}$). Both the sound scene simulation and NMF require the creation of two sound databases (figure  \ref{fig:blocDiagramNMF}). In parallel, a baseline method built from a frequency low-pass filter is computed. This method considers that road traffic is mainly composed of low frequencies and therefore can be filtered by a low-pass filter at the cut-off frequency $f_c$ (figure \ref{fig:blocDiagramFilter}). The performance of the frequency low-pass filter and NMF are then compared with the calculation of two metrics (Mean Absolute Error, normalized Root Mean Square Error).

@@

%\ml{faire une figure avec un diagrame de bloc et une section proposed approach avec des sub temps/frequence nmfsup nmfsemi}

@@

One of the main issue with the supervised approach is the generalization issue: how to be adapted to different sound mixtures with a fixed dictionary ? To better take account for the diverse nature of urban scenes, semi-supervised NMF can be useful as it has been proposed \cite{lee_semi-supervised_2010} to offer more flexibility. This method consists in composing the \textit{dictionary} with a fixed part $\mathbf{W_s} \in \mathbb{R}^+_{F\times K}$, composed in our case of spectrum representative of road traffic and with a mobile part, $\mathbf{W_r} \in \mathbb{R}^+_{F\times J}$ with $J <<K$, that is updated. Here, $J = 2$. The aim is to include in $\mathbf{W_r}$ the element that are not related with the traffic. The problem (\ref{eq:nmf}) become

@@

A last approach is tested based on unsupervised NMF. Usually, $\mathbf{W}$ is learnt with the help of a learning corpus by initiated it randomly. Here, as the concerned sound source is known and audio samples of car passages are available, a initial dictionary, $\mathbf{W_0}$, is learnt by converting the audio files in the spectra domain (see part \ref{part:dictionary_learning}). Then NMF is performed where $\mathbf{W}$ (eq. \ref{eq:updateW_unsup}) and $\mathbf{H}$ (eq.  \ref{eq:updateH_Sup}) are updated alternatively.

@@

Other thresholding methods as the \textit{soft} \cite{donoho1995noising}and the \textit{firm} \cite{fornasier2008iterative} and multiples way to display the distance through a sigmoïd or a Radial Basis Function have been investigated. A fast parametric study has revealed that the \textit{hard} tresholding method  with a linear representation of the similarity according to $K$ (see fig. \ref{fig:W_ThC_NMF}) was the best way to get better performances.

@@

This database is divided in two categories: $i)$ the \textit{event} category which are the brief sounds (from 1 to 20 seconds) that are considered as salient including 245 sound event samples divided in 19 sound classes (\textit{ringing bell, birds, sweeping broom, car horn, car passages, hammer, drill, coughing, barking dog, rolling suitcase, closing door, plane, siren, footstep, storm, street noise, train, tramway, truck and voice}) and $ii)$ the \textit{background} category that includes all the sounds that are of long duration and whose acoustic properties do not vary with respect to time. 154 sound samples belong to this category divided in 9 sound classes (\textit{birds, construction site noise, crowd, park, rain, children playing in schoolyard, constant traffic noise, ventilation, wind}). The sound class \textit{car passages} comes from 60 recordings of 2 cars made on the Ifsttar's runway on different speeds with multiple gear ratio. The other audio files have been found online (\textit{freesound.org}) and within the \textit{UrbanSound8k} database \cite{salamon_dataset_nodate}. Each sound classes are composed of multiples samples (\textit{bird01.wav}, \textit{bird02.wav} \dots). 
The software allows the user to control some parameters (number of events of each class that appear in the mixture, elapsed time between each sample of a same class, presence of a fade in and a fade out \dots) completed with a standard deviation that may brings some random behavior between the scenes. Furthermore, an audio file of each sound class present in the scene can be generated that allows to know its exact contribution as well as a text file that summarizes the time presence of all the events.\\

@@

with the \textit{Traffic Interference Ratio} $TIR = \left[-12, -6, 0, 6, 12\right]$. When $TIR = -12$, the traffic component is then less present than when $TIR = 12$ where it is predominant on the \textit{interfering} class. The 1 second equivalent sound pressure level, $p_{1s,traffic}$, is also calculated (figure \ref{fig:exampleScene}). Finally, the number of scenes designed is 750 (6 sub-corpus $\times$ 25 scenes $\times$  5 TPR values).

@@

The first estimator to determine the traffic sound level is the basic frequency low-pass filter which depend only on the cut-off frequencies $f_c$ = [500 1k 2k 5k 10k 20k] Hz. The spectrograms $\mathbf{V}$ are filtered and the remaining energy is then considered as traffic component (eq. \ref{eq:v_tr_filtered}).

@@

The second estimator is NMF. Multiples parameters are involved here between the building of the dictionary and the performed NMF.

@@

\begin{figure}[t!]
    \centering
    \begin{subfigure}[t]{0.47\linewidth}
        \centering
       \includegraphics[width=\linewidth]{../image/dictionary1.pdf}
        \caption{Sample of 3 seconds of a car passage}
        \label{fig:TIR_class_filter}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[t]{0.47\linewidth}
        \centering
       \includegraphics[width=\linewidth]{../image/dictionary2.pdf}
        \caption{Elements of the dictionary got for $w_t = 1$ second (3 spectrum) and  for $w_t = all$ (1 spectra) }
        \label{fig:TIR_class_filter}
    \end{subfigure}
\end{figure}

Each $k$ element of $\mathbf{W}$ is normalized such as $\vert \vert \mathbf{W_k} \vert \vert = 1$ with $\vert \vert \bullet \vert\vert$ the $\ell$-1 norm.\\
Table \ref{tab:dictionary_factors} summarizes the parameters and their related values.

@@

\subsubsection{Performed NMF}

Supervised and semi-supervised NMF are performed for 400 iterations which is sufficiently enough to get a stabilized reconstruction. ThC-NMF is performed on a lower number of iteration (60) to prevent $\mathbf{W}$ to not deviate to much from the initial dictionary. The spectrogram $\mathbf{V}$ and the dictionary $\mathbf{W}$ are expressed on two different spectral representation: with a linear frequency scale ($\Delta f \approx 10.8$ Hz) and with third octave bands (29 bands). Theses two methods are considered to compare a fine grain approach (the linear scale) with a coarser one (the third octave bands) as it reduces the number of frequency bins and allows to reduces the number of bands in the high frequencies where the traffic component is less present.  Furthermore, in the case of the linear frequency scale and for supervised and semi-supervised NMF, $\mathbf{V}$ and $\mathbf{W}$ are filtered at the frequencies $f_c$ in order to focused the reconstruction of the signal of the low frequency bins. Nevertheless, if NMF is performed with filtered elements ($\mathbf{V}_{f_c}$ and $\mathbf{W}_{f_c}$) to determine $\mathbf{H}_{f_c}$, the traffic signal reconstruction is done with the original dictionary $\mathbf{W}$, as

@@

With the third octave spectral representation, only the case $f_c = 20$ kHz is applied. Finally, for the ThC NMF, the threshold is define between 0.20 and 0.70 with a 0.01 step. Table \ref{tab:estimation_factors} summarizes the parameters and the related values.

@@

\subsubsection{Metrics}
The performances of the two estimators of the road traffic sound level are assessed through the calculation of two metrics.

\begin{itemize}

\item The Mean Absolute Error, $MAE$, expresses the quality of the long-term reconstruction of the signal. It consists in the average over the $N$ sound scenes of the absolute difference between the exact and estimated traffic sound level in dB,

@@

\item The normalized short-term Root Mean Square Error, $nRMSE$, calculates, for each sound scene, the error between the exact and estimated road traffic 1-s equivalent sound level of each file normalized by the 1-s equivalent sound level of the global scene, $p^t_{1s,global}$, in the linear scale,

\begin{equation}
nRMSE = \sqrt{\frac{1}{T}\sum_{t = 1}^T \left(\frac{p^t_{1s,traffic}-\tilde{p}^t_{1s,traffic}}{p^t_{1s,global}}\right)^2}
\end{equation}

where $T$ is the number of temporal bin in the signal. The linear scale is here more relevant as it is more sensitive to the error on the high sound levels than the dB scale. Then for one combination of factors, the $N$ $nRMSE$ calculated are averaged.\\
\end{itemize}

In all, according the table \ref{tab:dictionary_factors} and \ref{tab:estimation_factors}, 14040 settings are performed between the different form of the dictionary $\mathbf{W}$ (table \ref{tab:dictionary_factors}) and the multiple parameters taken into account by NMF.

@@

Table \ref{tab:results} summarized, according to the 3 main parameters (method, $\beta$ and spectral representation), the $MAE$ error averaged on all sub-classes and all $TIR$.\\

\begin{table*}[]
\centering
\begin{tabular}{@{}cccccccc@{}}
\toprule
$\mathbf{K}$ & $\mathbf{w_t}$ (s) & $\mathbf{f_c}$ (kHz) &\begin{tabular}[c]{@{}c@{}}\textbf{spectral} \\ \textbf{representation}\end{tabular} &  $\mathbf{\beta}$ & \textbf{method} & $\mathbf{t}$ & \textbf{$MAE$ (dB)} \\ \midrule
 &  & 20 &  &  & filter &  & 4.69 ($\pm$ 4.52) \\ 
 &  & 0.5 &  &  & filter &  & 2.89 ($\pm$ 2.84) \\ \hline \hline
25 & all & 0.5 & spectra & 1 & supervised NMF &  & \textbf{2.76 ($\pm$ 2.86)} \\ 
50 & 0.5 & 0.5 & spectra & 2 & supervised NMF &  & \textbf{2.56 ($\pm$ 2.48)} \\ 
50 & 0.5 &  20 & third octave & 1 & supervised NMF &  & 3.44 ($\pm$ 3.70) \\ 
50 & 0.5 & 20 & third octave & 2 & supervised NMF &  & 3.02 ($\pm$ 3.33) \\ \hline \hline
100 & 0.5 &  20 & spectra & 1 & semi-supervised NMF &  & \textbf{2.36 ($\pm$ 1.23)} \\ 
100 & 0.5 & 20 & spectra & 2 & semi-supervised NMF &  & \textbf{2.34 ($\pm$ 1.35)} \\ 
100 & 0.5  & 20 & third octave & 1 & semi-supervised NMF &  & \textbf{2.38 ($\pm$ 1.26)} \\ 
100 & 0.5 & 20 & third octave & 2 & semi-supervised NMF &  & \textbf{2.43 ($\pm$ 1.43)} \\ \hline \hline
50 & all & 5 & spectra & 1 & ThC NMF & 0.39 & \textbf{2.23 ($\pm$ 2.21)} \\ 
50 & all & 2 & spectra & 2 & ThC NMF & 0.37 & \textbf{2.17 ($\pm$ 2.28)} \\ 
100 & all & 20 & third octave & 1 & ThC NMF & 0.57 & \textbf{2.19 ($\pm$ 2.01)} \\ 
100 & all & 20 & third octave & 2 & ThC NMF & 0.54 & \textbf{2.16 ($\pm$ 2.24)}\\ \bottomrule
\end{tabular}
\caption{Best results according to $\beta$, method and  spectral representation}
\label{tab:results}
\end{table*}

The two first lines resume the error produced by the filter. $f_c = 20 $ kHz is equivalent to consider all the sound mixtures without distinguish the traffic from the others sound sources. Consequently , in low $TIR$ (-12 and -6), where traffic component is discreet, the error is more important than in high $TIR$ (6 and 12) where the traffic component is predominant. $f_c = 500$ Hz is the cut-off frequency with the lower mean error. It is then the baseline to refer to compare the performance of NMF. In low $TIR$, for \textit{alert} and \textit{animals}, sub-classes composed of higher frequencies, the impact of the filter is quite interesting as it suppress theses frequency components whereas for the other sub-classes where low frequencies are presents, the error as higher as the filter cannot dissociate the traffic element from the other sound sources. The sounds levels are then overestimate (figure \ref{fig:alert_-12}). In opposite, in high $TIR$, the low-pass filter removes too much energy from the traffic which has the consequence to underestimate the sound levels (figure \ref{fig:alert_12}).\\

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../image/LeqTrafficComparison_filter_alert_-12.pdf}
        \caption{}
        \label{fig:alert_-12}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../image/LeqTrafficComparison_filter_alert_12.pdf}
        \caption{}
        \label{fig:alert_12}
    \end{subfigure}

@@

The results of different versions of NMF are summarized next to the filter results with the NMF errors lower than the baseline in bold. With the exception of supervised NMF with third octave spectral representation, all NMF have a lower mean error than the baseline. The best combination is got with a ThC NMF with a third octave spectral representation, $\beta$ = 2 and a threshold $t$ = 0.54.

Between the dictionary parameters ($K$ and $w_t$) and the cut-off frequency $f_c$, no parameters is common to all the settings. For each method (supervised, semi-supervised and ThC NMF), the best scenario is detailed according the sub-classes and the $TIR$ (Figure \ref{fig:TIR_class_filter}, \ref{fig:TIR_class_sup}, \ref{fig:TIR_class_semi} and \ref{fig:W_ThC_NMF}).

>>>>

\section{Introduction}
\subsection{Related work}
With the introduction of the European Directive 2002/EC/49, cities over 100 000 inhabitants have to produce road traffic noise maps. These maps allow to estimate the number of city dwellers exposed to high noise levels and to draw up action plans to reduce it as too long exposures to these noises can generate health problems \cite{who_burden_2017}. These maps are the result of a simulation process based on the estimation of the traffic density on the main roads and the use of sound propagation techniques. They express $L_ {DEN}$ and $L_N$, which are \textit{Day-Evening-Night} and \textit{Night} equivalent A-weighted sound levels respectively. However, these maps introduce lot of uncertainty generated by the numerical tools \cite{van_leeuwen_noise_2015}, by the different calculation methodologies used \cite{leroy_uncertainty_2010}\cite{garg_critical_2014} or even by the calculation procedure of the number of inhabitants exposed to noise \cite{king_implementation_2011}. In addition, the usual road traffic noise maps are static, aggregating the exposure on the two indicators $L_{DEN}$ and $L_N$, thus ignoring the sound levels evolution throughout the day. Since the creation of road traffic noise maps entails long data collection and calculation times, the use of acoustic measurements could facilitate their updating or even the generation of dynamic maps \cite{wei_dynamic_2016}. These measurements can be performed at fixed stations spread all over the cities \cite{Mioduszewski} \cite{mietlicki2012innovative}, which would lead to the availability of the long-term evolution of the traffic noise levels. It can also be performed with  mobile stations \cite{can_exploring_2012} \cite{manvell2004sadmam} covering a larger area with fewer sensors but also sparse time periods. %The clustering between mobile and fixed measurements has been studied in \cite{can_measurement_2014}. \ml{je ne vois pas l'intéret de cette dernière phrase}

Currently, sensor networks in cities are spread for multiple applications (air quality assessment, measurement of meteorological parameters, ...), including the assessment of urban noise levels. DYNAMAP project \cite{dynamap_2016} studied the establishment and feasibility of such installations. It focuses on sensor installations on specific roads at the city scale in Milan and Rome \cite{bellucci_life_2017}. In a similar way, but reduced to few neighborhoods, the CENSE project\footnote{\url{http://cense.ifsttar.fr/}} \cite{picaut2017characterization} aims to combine \textit{in situ} observations, from a sensor network, and numerical data, from noise modeling, through data assimilation techniques.

If sensors networks could improve road traffic noise estimation compared with simulated maps, the issue of the correct estimation from  measurements of the traffic sound level is still unsolved \cite{Mioduszewski}. Indeed, the urban sound environment is a complex environment gathering lots of different sounds (car passages, voices, bird's whistles, car horn \dots) that can overlap. Consequently, the traffic sound level estimation based on measurements is not trivial task.
Many recent works have focused on the detection or recognition tasks of environmental sounds without distinction between them\cite{heittola_sound_2011}, \cite{defreville_automatic_2006}, \cite{dufaux_automatic_2000}, \cite{chu_environmental_2009}. A two step process is generally followed : describe the audio files with a set of features (Spectrum Gravity Spectrum, harmonicity, Mel-Frequency Cepstral Coefficient \dots) and classify them with the help of classifiers (Support Vector Machines, Gaussian Mixture Models, Hidden Markov Model, Artifical Neural Networks). A description of there features and classifiers can be found in \cite{cowling_comparison_2003} and their application can be found in \cite{shen_environmental_2012}, \cite{beritelli_pattern_2008}, \cite{couvreur_automatic_2004}. Recently, an Anomalous Noise Events Detector has been generated in \cite{socoro_anomalous_2017} to detect the sound sources from labeled recordings that are not related to the traffic component in order not to take them into account on the estimation of the traffic sound level. If the detection of the road traffic noise is good, the detection of these anomalous noise events stay weak and no information on the improvement on the estimation of the traffic nous level are presented.

@@

We propose in this paper a method based on the Non-Negative Matrix Factorization (NMF) technique to estimate the global, $\tilde{L}_{p,traffic}$, and the 1-s equivalent, $\tilde{p}_{1s,traffic}$ sound level of the traffic through the supervised and the semi-supervised approaches as well as a method using thresholding. To validate these approaches, we consider a corpus of simulated scenes artificially created with the simulator software \textit{simScene}. The use of simulated sound scenes is necessary as it offers a full control on the design of the scenes and the knowledge of the exact contribution of the traffic component which would hardly be extracted from a recording of an urban scene ($L_{p,traffic}$ and $p_{1s,traffic}$). Both the sound scene simulation and NMF require the creation of two sound databases (figure  \ref{fig:blocDiagramNMF}). In parallel, a baseline method built from a frequency low-pass filter is computed. This method considers that road traffic is mainly composed of low frequencies and therefore can be filtered by a low-pass filter at the cut-off frequency $f_c$ (figure \ref{fig:blocDiagramFilter}). The performance of the frequency low-pass filter and NMF are then compared with the calculation of two metrics (Mean Absolute Error, normalized Root Mean Square Error).

\begin{figure*}
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=.45\linewidth]{../image/bloc_diagram_NMF_EN.pdf}
        \caption{Frequency low-pass filter with $f_c$ = 500 Hz}
        \label{fig:TIR_class_filter}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=.45\linewidth]{../image/bloc_diagram_filtrage_EN.pdf}
        \caption{Block diagrams summed up the different step of the process for the frequency low-pass filter \ref{fig:blocDiagramFilter} and for NMF \ref{fig:blocDiagramNMF}}
		\label{fig:TIR_class_sup}
    \end{subfigure}
\end{figure*}

@@

@@

One of the main issue with the supervised approach is the generalization issue: how to be adapted to different sound mixtures with a fixed dictionary ? To better take into account the diverse nature of urban scenes, semi-supervised NMF can be useful as it has been proposed \cite{lee_semi-supervised_2010} to offer more flexibility. This method consists in composing the \textit{dictionary} with a fixed part $\mathbf{W_s} \in \mathbb{R}^+_{F\times K}$, composed in our case of spectrum representative of road traffic and with a mobile part, $\mathbf{W_r} \in \mathbb{R}^+_{F\times J}$ with $J <<K$, that is updated. Here, $J = 2$. The aim is to include in $\mathbf{W_r}$ the element that are not related with the traffic. The problem (\ref{eq:nmf}) become

@@

A last approach is tested based on unsupervised NMF. Usually, $\mathbf{W}$ is learnt with the help of a learning corpus by initiated it randomly. Here, as the concerned sound source is known and audio samples of car passages are available, a initial dictionary, $\mathbf{W_0}$, is learnt by converting the audio files in the spectra domain (see part \ref{part:dictionary_learning}). Then NMF is performed where $\mathbf{W}$ (eq. \ref{eq:updateW_unsup}) and $\mathbf{H}$ (eq.  \ref{eq:updateH_Sup}) are updated alternatively. $\mathbf{W}$ is therefore updated by forcing its initiation with \textit{a priori} knowledge.

@@

This approach is named \textit{Thresholded constraint NMF} (ThC NMF). Other thresholding methods as the \textit{soft} \cite{donoho1995noising}and the \textit{firm} \cite{fornasier2008iterative} and multiples way to display the distance through a sigmoïd or a Radial Basis Function have been investigated. A fast parametric study has revealed that the \textit{hard} thresholding method  with a linear representation of the similarity according to $K$ (see fig. \ref{fig:W_ThC_NMF}) was the best way to get better performances.

@@

This database is divided in two categories: $i)$ the \textit{event} category which are the brief sounds (from 1 to 20 seconds) that are considered as salient including 245 sound event samples divided in 19 sound classes (\textit{ringing bell, birds, sweeping broom, car horn, car passages, hammer, drill, coughing, barking dog, rolling suitcase, closing door, plane, siren, footstep, storm, street noise, train, tramway, truck and voice}) and $ii)$ the \textit{background} category that includes all the sounds that are of long duration and whose acoustic properties do not vary with respect to time. 154 sound samples belong to this category divided in 9 sound classes (\textit{birds, construction site noise, crowd, park, rain, children playing in schoolyard, constant traffic noise, ventilation, wind}). The sound class \textit{car passages} comes from 60 recordings of 2 cars made on the Ifsttar's runway on different speeds with multiple gear ratio. The other audio files have been found online (\textit{freesound.org}) and within the \textit{UrbanSound8k} database \cite{salamon_dataset_nodate}. Each sound classes is composed of multiples samples (\textit{bird01.wav}, \textit{bird02.wav} \dots). 
The software allows the user to control some parameters (number of events of each class that appear in the mixture, elapsed time between each sample of a same class, presence of a fade in and a fade out \dots) completed with a standard deviation that may bring some random behavior between the scenes. Furthermore, an audio file of each sound class present in the scene can be generated that allows to know its exact contribution as well as a text file that summarizes the time presence of all the events.\\

@@

with the \textit{Traffic Interference Ratio} $TIR = \left[-12, -6, 0, 6, 12\right]$. When $TIR = -12$, the traffic component is then less present than when $TIR = 12$ where it is predominant on the \textit{interfering} class. The 1 second equivalent sound pressure level, $p_{1s,traffic}$, is also calculated (figure \ref{fig:exampleScene}). The total number of scenes designed is 750 (6 sub-corpus $\times$ 25 scenes $\times$  5 TIR values).

@@

The first estimator to determine the traffic sound level is a basic frequency low-pass filter which depend only on the cut-off frequencies $f_c$ = [500 1k 2k 5k 10k 20k] Hz. The spectrograms $\mathbf{V}$ are filtered and the remaining energy is then considered as traffic component (eq. \ref{eq:v_tr_filtered}).

@@

The second estimator is NMF. Multiples parameters are involved here between the dictionary learning and the own parameters of the NMF.

@@

\begin{figure}[t!]
    \centering
    \begin{subfigure}[t]{0.47\linewidth}
        \centering
       \includegraphics[width=\linewidth]{../image/dictionary1.pdf}
        \caption{Sample of 3 seconds of a car passage}
        \label{fig:specW}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[t]{0.47\linewidth}
        \centering
       \includegraphics[width=\linewidth]{../image/dictionary2.pdf}
        \caption{Elements of the dictionary got for $w_t = 1$ second (3 spectrum) and  for $w_t = all$ (1 spectra) }
        \label{fig:ElementW}
    \end{subfigure}
\end{figure}

Each $k$ element of $\mathbf{W}$ is normalized such as $\vert \vert \mathbf{W_k} \vert \vert = 1$ with $\vert \vert \bullet \vert\vert$ the $\ell$-1 norm.\\

Table \ref{tab:dictionary_factors} summarizes the parameters and their related values.

@@

\subsubsection{NMF parameters}

Supervised and semi-supervised NMF are performed for 400 iterations which is sufficiently enough to get a stabilized reconstruction. ThC-NMF is performed on a lower number of iteration (60) to prevent $\mathbf{W}$ to not deviate too much from the initial dictionary. The spectrogram $\mathbf{V}$ and the dictionary $\mathbf{W}$ are expressed on two different spectral representations: with a linear frequency scale ($\Delta f \approx 10.8$ Hz) and with third octave bands (29 bands). These two methods are considered to compare a fine grain approach (the linear scale) with a coarser one (the third octave bands) as it reduces the number of frequency bins in the high frequencies where the traffic component is less present and generates less calculations. Furthermore, in the case of the linear frequency scale and for supervised and semi-supervised NMF, $\mathbf{V}$ and $\mathbf{W}$ are filtered at the frequencies $f_c$ in order to focused the reconstruction of the signal of the low frequency bins. Nevertheless, if NMF is performed with filtered elements ($\mathbf{V}_{f_c}$ and $\mathbf{W}_{f_c}$) to determine $\mathbf{H}_{f_c}$, the traffic signal reconstruction is done with the original dictionary $\mathbf{W}$, as

@@

With the third octave spectral representation, only the case $f_c = 20$ kHz is applied. For the ThC NMF, the threshold is define between 0.20 and 0.70 with a 0.01 step. Table \ref{tab:estimation_factors} summarizes the parameters and their related values.

@@

\subsubsection{Metrics}
The performances of the two estimators of the road traffic sound level are assessed through the calculation of one metric, the Mean Absolute Error ($MAE$). It expresses the quality of the long-term reconstruction of the signal. It consists in the average over the $N$ sound scenes of the absolute difference between the exact and estimated traffic sound level in dB,

@@

In all, according Tables \ref{tab:dictionary_factors} and \ref{tab:estimation_factors}, 24540 settings are performed between the different form of the dictionary $\mathbf{W}$ (table \ref{tab:dictionary_factors}) and the multiple parameters taken into account by NMF:  for the filter estimator, between the $TIR$, the sub-classes and $f_c$, 180 settings are performed whereas for supervised and semi-supervised, 7560 associations of parameters are made. For ThC NMF, 16800 combinations can be calculated.

@@

Table \ref{tab:results} summarized, according to the 3 main parameters (method, $\beta$ and spectral representation), the $MAE$ error averaged on all sub-classes and all $TIR$ (750 sound mixtures in all).\\

\begin{table*}[]
\centering
\begin{tabular}{@{}cccccccc@{}}
\toprule
$\mathbf{K}$ & $\mathbf{w_t}$ (s) & $\mathbf{f_c}$ (kHz) &\begin{tabular}[c]{@{}c@{}}\textbf{spectral} \\ \textbf{representation}\end{tabular} &  $\mathbf{\beta}$ & \textbf{method} & $\mathbf{t}$ & \textbf{$MAE$ (dB)} \\ \midrule
 &  & 20 &  &  & filter &  & 4.69 ($\pm$ 4.52) \\ 
 &  & 0.5 &  &  & filter &  & 2.89 ($\pm$ 2.84) \\ \hline \hline
25 & all & 0.5 & linear & 1 & supervised NMF &  & \textbf{2.76 ($\pm$ 2.86)} \\ 
50 & 0.5 & 0.5 & linear & 2 & supervised NMF &  & \textbf{2.56 ($\pm$ 2.48)} \\ 
50 & 0.5 &  20 & third octave & 1 & supervised NMF &  & 3.44 ($\pm$ 3.70) \\ 
50 & 0.5 & 20 & third octave & 2 & supervised NMF &  & 3.02 ($\pm$ 3.33) \\ \hline \hline
100 & 0.5 &  20 & linear & 1 & semi-supervised NMF &  & \textbf{2.36 ($\pm$ 1.23)} \\ 
100 & 0.5 & 20 & linear & 2 & semi-supervised NMF &  & \textbf{2.34 ($\pm$ 1.35)} \\ 
100 & 0.5  & 20 & third octave & 1 & semi-supervised NMF &  & \textbf{2.38 ($\pm$ 1.26)} \\ 
100 & 0.5 & 20 & third octave & 2 & semi-supervised NMF &  & \textbf{2.43 ($\pm$ 1.43)} \\ \hline \hline
50 & all & 5 & linear & 1 & ThC NMF & 0.39 & \textbf{2.23 ($\pm$ 2.21)} \\ 
50 & all & 2 & linear & 2 & ThC NMF & 0.37 & \textbf{2.17 ($\pm$ 2.28)} \\ 
100 & all & 20 & third octave & 1 & ThC NMF & 0.57 & \textbf{2.19 ($\pm$ 2.01)} \\ 
100 & all & 20 & third octave & 2 & ThC NMF & 0.54 & \textbf{2.16 ($\pm$ 2.24)}\\ \bottomrule
\end{tabular}
\caption{Best results according to $\beta$, method and  spectral representation}
\label{tab:results}
\end{table*}

The two first lines resume the error produced by the filter. $f_c = 20 $ kHz is equivalent to consider all the sound mixtures without distinguishing the traffic from the others sound sources. Consequently , in low $TIR$ (-12 and -6), where traffic component is discreet, the error is more important than in high $TIR$ (6 and 12) where the traffic component is predominant. $f_c = 500$ Hz is the cut-off frequency with the lower mean error obtained. It is then the baseline that will be used to compare the performances of NMF. In low $TIR$, for \textit{alert} and \textit{animals}, sub-classes composed of higher frequencies, the filter is efficient as it suppress these frequency components whereas for the other sub-classes where low frequencies are present, the error is higher as the filter considers all the energy located in the pass-band and then do not dissociate the traffic element from the other sound sources. The sounds levels are then overestimate (figure \ref{fig:alert_-12}). In opposite, in high $TIR$, a low-pass filter at $f_c$ = 500 Hz removes too much energy from the traffic which has the consequence to underestimate the sound levels (figure \ref{fig:alert_12}).\\

\begin{figure*}[t]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../image/LeqTrafficComparison_filter_alert_-12.pdf}
        \caption{}
        \label{fig:alert_-12}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{../image/LeqTrafficComparison_filter_alert_12.pdf}
        \caption{}
        \label{fig:alert_12}
    \end{subfigure}

@@

The results of different versions of NMF are summarized next to the filter results in Table \ref{tab:results_TIR}. NMF errors lower than the baseline are put in bold letter. With the exception of supervised NMF with third octave spectral representation, all NMF have a lower mean error than the baseline. The best combination is got with a ThC NMF with a third octave spectral representation, $\beta$ = 2 and a threshold $t$ = 0.54.

Between the dictionary parameters ($K$ and $w_t$) and the cut-off frequency $f_c$, none is common to all the settings. If for the third octave spectral representation, $f_c$ has been fixed at 20 kHz, in linear representation, this parameters is variable depending on chosen method.
